Revisiting~the~Classics: Online~RL~in~the~Programmable~Dataplane

### 2021-05-03 paper/paper.tex
Modifying runner now that the hash table apparently works?

@@

Policy sizes are set to those matching a real-world DDoS control application~\parencite{DBLP:journals/tnsm/SimpsonRP20}: 20-dimension state vectors, a bias tile and 16 full tiling sets (7$\times$1-dim, 8$\times$2-dim, 1$\times$4-dim), 8 tilings per dimension set, 6 tiles per dimension, choosing between 10 actions.
Although their more successful \emph{SPF} agent design uses 4 actions, we choose this to investigate the performance of larger agent designs.

@@

\fakepara{The impact of bit depth}
We further investigate how bit depth affects the accuracy of policy by varying the number of bits used to represent the mantissa of action values and input state.

@@

\begin{table}
	\caption{Throughput and per-item compute time for an RL agent with/without policy learning. State$\rightarrow$action latency equals the offline completion cost. TODO: compare to host machine? Put completion times first? Put multi first?\label{tab:lat-tput}}
	\resizebox{\linewidth}{!}{
		\expandableinput ../tables/build/latency-tput
	}
\end{table}

@@

\fakepara{The impact of bit depth}
?? \Cref{fig:quant-acc}
?? \SI{5}{\bit} mantissa suffices for $\ge$ \SI{90}{\percent} relative accuracy, so \SI{8}{\bit} is fine (1S + 2E + 5M), \SI{16}{\bit} is better.

\begin{figure}
	\includegraphics{../plots/build/marl-quant/accuracy-binary}
	\caption{Normalised accuracy of a converted, pre-trained floating-point tile-coded policy after conversion to $32Qn$ fixed-point.}\label{fig:quant-acc}
\end{figure}

>>>>

?? Probably mention the idea of including "state keys" and "reward keys" in the input state vector.

@@

Policy sizes are set to those matching a real-world DDoS control application~\parencite{DBLP:journals/tnsm/SimpsonRP20}: 20-dimension state vectors, a bias tile and 16 full tiling sets (7$\times$1-dim, 8$\times$2-dim, 1$\times$4-dim), 8 tilings per dimension set, 6 tiles per dimension, choosing between 10 actions.
Although their more successful \emph{SPF} agent design uses 3 actions, we choose this to investigate the performance of larger agent designs.

@@

%\fakepara{The impact of bit depth}
%We further investigate how bit depth affects the accuracy of policy by varying the number of bits used to represent the mantissa of action values and input state.

@@

\begin{table}
	\caption{Throughput and per-item compute time for an RL agent with/without policy learning. State$\rightarrow$action latency equals the offline completion cost. TODO: compare to host machine? Put completion times first? Put multi first?\label{tab:lat-tput}}
	\resizebox{\linewidth}{!}{
		\expandableinput ../tables/build/latency-tput-temp
	}
\end{table}

@@

%\fakepara{The impact of bit depth}
%?? \Cref{fig:quant-acc}
%?? \SI{5}{\bit} mantissa suffices for $\ge$ \SI{90}{\percent} relative accuracy, so \SI{8}{\bit} is fine (1S + 2E + 5M), \SI{16}{\bit} is better.
%
%\begin{figure}
%	\includegraphics{../plots/build/marl-quant/accuracy-binary}
%	\caption{Normalised accuracy of a converted, pre-trained floating-point tile-coded policy after conversion to $32Qn$ fixed-point.}\label{fig:quant-acc}
%\end{figure}
